Printer ballistics through texture analysis of characters

### 2013-11-28 Printer_Ballistics.tex
Appendix
Before lunch

@@

\appendix

>>>>

Details on how to calculate values of contrast, correlation, energy and homogeneity can be seen in Appendix A.

@@

\appendix
\label{app:Appendix A}

\section{Formulas}
\subsection{Contrast}

Returns the measure of contrast between the pixel of interest and neighboring pixel. For a constant image (same shade of gray to the full extent) the value is 0.

$$\sum_{i,j}\vert i - j \lvert^2 p(i,j)$$

\subsection{Co-relation}

Returns the measure of how much the pixel is related to its neighbor. The range is from -1 to 1, where 1 means a fully correlated and -1, totally uncorrelated image.

$$\sum_{i,j} \frac{(i - \mu i) (j - \mu j) p(i,j)} {\sigma_i \sigma_j}$$

\subsection{Energy}

Returns the sum of squared raised elements within the array. The range of possible values is from 0 to 1. A constant image (same shade of gray in all its extension) has value 1.

$$\sum_{i,j} p(i, j)^2$$
